---
title: "Tidy 311"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Step 7

### Ingesting Data
```{r}
library(ggplot2)
library(dplyr)
library(readr)
library(tidyverse)
library(reshape)
data = read_csv("https://data.cityofnewyork.us/resource/erm2-nwe9.csv?%24select=Created_Date,Agency,Complaint_Type,Incident_Address,Location")
```

### What makes the data messy?
```{r}
str(data)
```
* The latitude and longitude are in the same column.
* The minute, hour, day, year, and month are in the same column.

### Separating Latitude & Longitude
```{r}
data = data %>% extract(Location, c('Latitude', 'Longitude'), '\\((.*) (.*)\\)', convert = TRUE) 
```

### Separating House Number & Street Name
```{r}
data = data %>% extract(Incident_Address, c('House Number', 'Street'), '(\\S+)\\s+(.*)', convert = TRUE) 
```
This splits the address at the first space, but it does not work perfectly. Some of the addresses do not contain a house number, as in row 18, in this case "ESSEX STREET" becomes "ESSEX" and "STREET".

### Separating Date and Time
```{r}
data$Date = as.Date(data$Created_Date)
data$Time = format(data$Created_Date,"%H:%M:%S")
```

### Viewing Results
```{r}
head(data, 20)
```


__Some R code modified from StackOverflow.com__
